A Comparison of Graph Processing Systems

### 2020-09-06 documentation/paper/sections/results/galoisSpeedup.tex
new Hugepage plots and updated speedups

>>>>

\section{Hugepages}
\begin{figure}
	\includegraphics[width=\linewidth]{../../plots/singleNodeSSSPGaloisHPThreads.png}
	\caption{Calculation time speedup with increasing thread count for Galois Single-source Shortest-paths with Hugepages}
	\label{fig:galoisHPSpeedupSSSP}
\end{figure}

\begin{figure}
	\includegraphics[width=\linewidth]{../../plots/singleNodeBFSGaloisHPThreads.png}
	\caption{Calculation time speedup with increasing thread count for Galois Breadth-first search with Hugepages}
	\label{fig:galoisHPSpeedupBFS}
\end{figure}

\begin{figure}
	\begin{subfigure}{\columnwidth}
		\includegraphics[width=\linewidth]{../../plots/singleNodePRPullGaloisHPThreads.png}
		\caption{PageRank Pull}
		\label{fig:galoisHPSpeedupPRPull}
	\end{subfigure}
	\begin{subfigure}{\columnwidth}
		\includegraphics[width=\linewidth]{../../plots/singleNodePRPushGaloisHPThreads.png}
		\caption{PageRank Push}
		\label{fig:galoisHPSpeedupPRPush}
	\end{subfigure}
	\caption{Calculation time speedup with increasing thread count for Galois PageRank Push and Pull algorithms using Hugepages.}
\end{figure}
